---
title: "uschange"
author: "Julien JACQUES"
date: "2/19/2020"
output: pdf_document
---

# Income

```{r, message=FALSE, warning=FALSE}
library(fpp2)
income=uschange[,"Income"]
autoplot(income)
```


We see no trend and no seasonal pattern... We can check the ACF 
```{r}
ggAcf(income)
ggPacf(income)
```

It seems to be no correlation or auto-correlation... 
We can check that with a Box.test:
```{r}
Box.test(income,lag=10,type="Ljung-Box")
```

Indeed, no reason to reject the fact that it is a white noise : there is nothing to forecast in this series !!

# Unemployment

```{r}
library(fpp2)
unemp=uschange[,"Unemployment"]
autoplot(unemp)
Box.test(unemp,lag=10,type="Ljung-Box")
ggAcf(unemp)
ggPacf(unemp)
```

Maybe an $AR_8$ ?

```{r}
ar8=Arima(unemp,order=c(8,0,0))
print(ar8)
```

We can check the residual
```{r}
checkresiduals(ar8)
```

The residual are a white noise, we can keep this model for our forecast.

```{r}
autoplot(forecast(ar8,h=12))
```

# All 5 series togheter

```{r}
usc_train=window(uschange,start=c(1970,1),end=c(2015,4))
usc_test=window(uschange,start=c(2016,1),end=c(2016,3))
```

We use Vectorial Auto-Regressive models. We choose the order with VARselect function :
```{r, message=FALSE, warning=FALSE}
library(vars)
VARselect(usc_train, lag.max=10, type="const")
```

AIC leads to select an order equal to 3:
```{r}
var <- VAR(usc_train, p=3,type = "const")
prev=forecast(var,h=3,PI=FALSE)
plot(prev)
print(sqrt(mean((prev$forecast$Consumption$mean-usc_test[,"Consumption"])^2)))
print(sqrt(mean((prev$forecast$Income$mean-usc_test[,"Income"])^2)))
print(sqrt(mean((prev$forecast$Production$mean-usc_test[,"Production"])^2)))
print(sqrt(mean((prev$forecast$Savings$mean-usc_test[,"Savings"])^2)))
print(sqrt(mean((prev$forecast$Unemployment$mean-usc_test[,"Unemployment"])^2)))
```

We could compare to univariate SARIMA models...
```{r}
fit <- auto.arima(usc_train[,"Consumption"])
prev=forecast(fit,h=3)
print(sqrt(mean((prev$mean-usc_test[,"Consumption"])^2)))
fit <- auto.arima(usc_train[,"Income"])
prev=forecast(fit,h=3)
print(sqrt(mean((prev$mean-usc_test[,"Income"])^2)))
fit <- auto.arima(usc_train[,"Production"])
prev=forecast(fit,h=3)
print(sqrt(mean((prev$mean-usc_test[,"Production"])^2)))
fit <- auto.arima(usc_train[,"Savings"])
prev=forecast(fit,h=3)
print(sqrt(mean((prev$mean-usc_test[,"Savings"])^2)))
fit <- auto.arima(usc_train[,"Unemployment"])
prev=forecast(fit,h=3)
print(sqrt(mean((prev$mean-usc_test[,"Unemployment"])^2)))
```

The results are better with univariate time series ! Probably because we have more flexible models for univariate models (MA part, seasonal part...)  



